Adopting agile in the large: motivations, success factors and challenges

### 2014-04-27 journal/article.tex
Challenges

>>>>

\subsubsection{Modes of transformation}

Top down

Bottom up

Big bang

Transitional

\subsection{Challenges in transformation}

Any organizational transformation involving numerous individuals will face some
challenges. As stated by Research Question 3, we investigated what are typical
challenges that large organizations introducing agile methods face.

Challenges can be organized on a high level into three categories. First we
discuss challenges relating to managing the transformation. These challenges
relate to managing people and resourcing. Secondly we present challenges in
choosing and establishing a suitable agile model. Thirdly challenges related to
large organization size are presented. Size will bring challenges such as
coordinating work between many teams and adapting other functions than
development to agile.

\subsubsection{Challenges caused by management of the transformation}

In the beginning of the transformation the organization has realized the need to
change and is going towards the initial push.
In many cases the initiative to change came from management, but when presented
wrong the initiative becomes a mandate. Spayd summarizes this as:
``Organizations do not change merely because the boss says so, at least not in
the way that is intended'' [P49]. In that organization the introduction of CMM
was carried out consistently by a mandate, but the collaborative nature of agile
did not comply with such a mindset. A top down mandate may also dilute the
understanding of the reasons for starting the transformation, and further for
agile development overall [P2].

Organizations had bad experiences with prescribing how to carry out Scrum
practices. For instance, doing agile based on checklists would not work [P41].
Benefield described that it was challenging to find a balance between
independence for teams to choose their way and diluting the value and structure
of Scrum [P6]. Giving room for team autonomy was seen

% Lack of plans (a guess -- not included)?

%%%%%%%%%%%%%%%%%%%%%%%%%%%

% ---------------------------------------------------------------------
